Simulating High-Dimensional Multivariate Data using the Bigsimr R Package

### 2021-10-19 arXiv_bigsimr/arXiv_bigsimr.tex
arXiv echoing and warnings

\author{
    David S. Hippocampus
    \thanks{Use footnote for providing further information about author
(webpage, alternative address)---\emph{not} for acknowledging funding
agencies. Optional.}
   \\
    Department of Computer Science \\
    Cranberry-Lemon University \\
  Pittsburgh, PA 15213 \\
  \texttt{\href{mailto:hippo@cs.cranberry-lemon.edu}{\nolinkurl{hippo@cs.cranberry-lemon.edu}}} \\
   \And
    Elias D. Striatum
   \\
    Department of Electrical Engineering \\
    Mount-Sheikh University \\
  Santa Narimana, Levand \\
  \texttt{\href{mailto:stariate@ee.mount-sheikh.edu}{\nolinkurl{stariate@ee.mount-sheikh.edu}}} \\
  }

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{2020{-}02{-}25}\NormalTok{)}
\NormalTok{num\_genes    }\OtherTok{\textless{}{-}} \DecValTok{3}
\NormalTok{num\_patients }\OtherTok{\textless{}{-}} \DecValTok{5}
\NormalTok{gene\_sample  }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(example\_genes[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{1000}\NormalTok{], num\_genes)}

\NormalTok{cap }\OtherTok{\textless{}{-}} \FunctionTok{paste0}\NormalTok{(}\StringTok{"mRNA expression for three selected high{-}expressing genes, "}\NormalTok{,}
              \FunctionTok{paste}\NormalTok{(gene\_sample, }\AttributeTok{collapse =} \StringTok{", "}\NormalTok{), }
              \StringTok{", for the first five patients in the TCGA BRCA data set."}\NormalTok{)}

\NormalTok{small\_brca }\OtherTok{\textless{}{-}}\NormalTok{ example\_brca }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(}\FunctionTok{all\_of}\NormalTok{(gene\_sample)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{head}\NormalTok{(}\AttributeTok{n =}\NormalTok{ num\_patients) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{as\_tibble}\NormalTok{(}\AttributeTok{rownames =} \StringTok{"Patient ID"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Patient ID}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{str\_sub}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Patient ID}\StringTok{\textasciigrave{}}\NormalTok{, }\AttributeTok{end =} \DecValTok{12}\NormalTok{))}

\NormalTok{small\_brca }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{kable}\NormalTok{(}\AttributeTok{format =} \StringTok{"latex"}\NormalTok{, }\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{caption =}\NormalTok{ cap)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{ggpairs}\NormalTok{(}
  \AttributeTok{data =}\NormalTok{ example\_brca[, gene\_sample],}
  \AttributeTok{upper =} \FunctionTok{list}\NormalTok{(}\AttributeTok{continuous =} \FunctionTok{wrap}\NormalTok{(}\StringTok{\textquotesingle{}cor\textquotesingle{}}\NormalTok{, }\AttributeTok{method =} \StringTok{"spearman"}\NormalTok{))}
\NormalTok{) }\SpecialCharTok{+} 
  \FunctionTok{theme\_bw}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.text.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{angle =} \SpecialCharTok{{-}}\DecValTok{90}\NormalTok{, }\AttributeTok{vjust =} \FloatTok{0.5}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in cor.test.default(x, y, method = method, use = use): Cannot compute
## exact p-value with ties

## Warning in cor.test.default(x, y, method = method, use = use): Cannot compute
## exact p-value with ties

## Warning in cor.test.default(x, y, method = method, use = use): Cannot compute
## exact p-value with ties
\end{verbatim}

@@

\begin{verbatim}
## Julia version 1.5.3 at location /Applications/Julia-1.5.app/Contents/Resources/julia/bin will be used.
\end{verbatim}

\begin{verbatim}
## Loading setup script for JuliaCall...
\end{verbatim}

\begin{verbatim}
## Finish loading setup script for JuliaCall.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{p0 }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(df, }\FunctionTok{aes}\NormalTok{(Temp, Ozone)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{size =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Temperature"}\NormalTok{)}

\NormalTok{pTemp }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(df, }\FunctionTok{aes}\NormalTok{(Temp)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_density}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.title.y =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.text =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.ticks =} \FunctionTok{element\_blank}\NormalTok{())}

\NormalTok{pOzone }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(df, }\FunctionTok{aes}\NormalTok{(Ozone)) }\SpecialCharTok{+} 
    \FunctionTok{geom\_density}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.y =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.ticks =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.text =} \FunctionTok{element\_blank}\NormalTok{()) }\SpecialCharTok{+}
  \FunctionTok{coord\_flip}\NormalTok{()}

\NormalTok{pTemp }\SpecialCharTok{+} \FunctionTok{plot\_spacer}\NormalTok{() }\SpecialCharTok{+}\NormalTok{ p0 }\SpecialCharTok{+}\NormalTok{ pOzone }\SpecialCharTok{+} 
  \FunctionTok{plot\_layout}\NormalTok{(}\AttributeTok{widths =} \FunctionTok{c}\NormalTok{(}\DecValTok{3}\NormalTok{,}\DecValTok{1}\NormalTok{), }\AttributeTok{heights =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{3}\NormalTok{)) }
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## Julia Object of type NamedTuple{(:lower, :upper),Tuple{Float64,Float64}}.
## (lower = -0.8806384281235534, upper = 0.880733034303322)
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{p1 }\OtherTok{\textless{}{-}}\NormalTok{ df\_sim }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(Temp, Ozone)) }\SpecialCharTok{+}
  \FunctionTok{geom\_density\_2d\_filled}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"none"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Simulated Temperature"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Simulated Ozone"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\FunctionTok{max}\NormalTok{(df}\SpecialCharTok{$}\NormalTok{Ozone))) }\SpecialCharTok{+}
  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{limits =} \FunctionTok{range}\NormalTok{(df}\SpecialCharTok{$}\NormalTok{Temp))}

\NormalTok{p1Temp }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(df\_sim, }\FunctionTok{aes}\NormalTok{(Temp)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_density}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{fill =} \StringTok{"lightseagreen"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.title.y =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.text =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.ticks =} \FunctionTok{element\_blank}\NormalTok{())}

\NormalTok{p1Ozone }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(df\_sim, }\FunctionTok{aes}\NormalTok{(Ozone)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_density}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{fill =} \StringTok{"lightseagreen"}\NormalTok{) }\SpecialCharTok{+} 
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.y =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.title.x =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.ticks =} \FunctionTok{element\_blank}\NormalTok{(),}
        \AttributeTok{axis.text =} \FunctionTok{element\_blank}\NormalTok{()) }\SpecialCharTok{+}
  \FunctionTok{coord\_flip}\NormalTok{() }

\NormalTok{p1Temp }\SpecialCharTok{+} \FunctionTok{plot\_spacer}\NormalTok{() }\SpecialCharTok{+}\NormalTok{ p1 }\SpecialCharTok{+}\NormalTok{ p1Ozone }\SpecialCharTok{+} 
  \FunctionTok{plot\_layout}\NormalTok{(}\AttributeTok{widths =} \FunctionTok{c}\NormalTok{(}\DecValTok{3}\NormalTok{,}\DecValTok{1}\NormalTok{), }\AttributeTok{heights =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{3}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: Removed 388 rows containing non-finite values (stat_density2d_filled).
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{bivariate\_normal\_sims }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(rho, rho\_hat, }\AttributeTok{color =}\NormalTok{ type)) }\SpecialCharTok{+}
    \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
    \FunctionTok{geom\_abline}\NormalTok{(}\AttributeTok{slope =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ type }\SpecialCharTok{+}\NormalTok{ N) }\SpecialCharTok{+} 
    \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{bivariate\_gamma\_sims }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(rho, rho\_hat, }\AttributeTok{color =}\NormalTok{ type)) }\SpecialCharTok{+}
    \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
    \FunctionTok{geom\_abline}\NormalTok{(}\AttributeTok{slope =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ type }\SpecialCharTok{+}\NormalTok{ N) }\SpecialCharTok{+} 
    \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{bivariate\_nbinom\_sims }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(rho, rho\_hat, }\AttributeTok{color =}\NormalTok{ type)) }\SpecialCharTok{+}
    \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
    \FunctionTok{geom\_abline}\NormalTok{(}\AttributeTok{slope =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ type }\SpecialCharTok{+}\NormalTok{ N) }\SpecialCharTok{+} 
    \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{allDat }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(}
    \FunctionTok{select}\NormalTok{(bivariate\_normal\_sims, margins, type, N, rho, rho\_hat),}
    \FunctionTok{select}\NormalTok{(bivariate\_gamma\_sims, margins, type, N, rho, rho\_hat),}
    \FunctionTok{select}\NormalTok{(bivariate\_nbinom\_sims, margins, type, N, rho, rho\_hat)}
\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{margins =} \FunctionTok{factor}\NormalTok{(margins, }\AttributeTok{levels=}\FunctionTok{c}\NormalTok{(}\StringTok{"norm"}\NormalTok{, }\StringTok{"gamma"}\NormalTok{, }\StringTok{"nbinom"}\NormalTok{)),}
           \AttributeTok{type =} \FunctionTok{factor}\NormalTok{(type, }\AttributeTok{levels=}\FunctionTok{c}\NormalTok{(}\StringTok{"Pearson"}\NormalTok{, }\StringTok{"Spearman"}\NormalTok{, }\StringTok{"Kendall"}\NormalTok{)),}
           \AttributeTok{N =} \FunctionTok{factor}\NormalTok{(N))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{tabMAE }\OtherTok{\textless{}{-}}\NormalTok{ allDat }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{group\_by}\NormalTok{(N, type, margins) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{summarize}\NormalTok{(}\AttributeTok{MAE =} \FunctionTok{mean}\NormalTok{(}\FunctionTok{abs}\NormalTok{(rho }\SpecialCharTok{{-}}\NormalTok{ rho\_hat))) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{ungroup}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## `summarise()` regrouping output by 'N', 'type' (override with `.groups` argument)
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{kable}\NormalTok{(tabMAE, }\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{format =} \StringTok{"latex"}\NormalTok{,}
      \AttributeTok{linesep =} \FunctionTok{c}\NormalTok{(}\StringTok{""}\NormalTok{, }\StringTok{""}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{addlinespace"}\NormalTok{),}
      \AttributeTok{col.names =} \FunctionTok{c}\NormalTok{(}\StringTok{"No. of random vectors"}\NormalTok{,}
                    \StringTok{"Correlation type"}\NormalTok{,}
                    \StringTok{"Distribution"}\NormalTok{,}
                    \StringTok{"Mean abs. error"}\NormalTok{),}
      \AttributeTok{caption =} \StringTok{"Average abolute error in matching the target dependency across the entire range of possible correlations for each bivariate marginal."}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# https://www.datanovia.com/en/blog/how{-}to{-}change{-}ggplot{-}facet{-}labels/}
\CommentTok{\# New facet label names}
\NormalTok{repsLabs }\OtherTok{\textless{}{-}} \FunctionTok{paste0}\NormalTok{(}\StringTok{"B="}\NormalTok{, }\FunctionTok{c}\NormalTok{(}\StringTok{"1,000"}\NormalTok{, }\StringTok{"10,000"}\NormalTok{, }\StringTok{"100,000"}\NormalTok{) )}
\FunctionTok{names}\NormalTok{(repsLabs) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{10000}\NormalTok{, }\DecValTok{100000}\NormalTok{)}
\NormalTok{typeLabs }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Pearson"}\NormalTok{, }\StringTok{"Spearman"}\NormalTok{, }\StringTok{"Kendall"}\NormalTok{)}
\FunctionTok{names}\NormalTok{(typeLabs) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"Pearson"}\NormalTok{, }\StringTok{"Spearman"}\NormalTok{, }\StringTok{"Kendall"}\NormalTok{)}

\CommentTok{\# Set colors}
\DocumentationTok{\#\# RColorBrewer::display.brewer.all()}
\NormalTok{numColors }\OtherTok{\textless{}{-}} \DecValTok{4}
\NormalTok{numGroups }\OtherTok{\textless{}{-}} \FunctionTok{length}\NormalTok{(}\FunctionTok{levels}\NormalTok{(allDat}\SpecialCharTok{$}\NormalTok{margins))}
\NormalTok{myColors }\OtherTok{\textless{}{-}} \FunctionTok{rev}\NormalTok{(RColorBrewer}\SpecialCharTok{::}\FunctionTok{brewer.pal}\NormalTok{(}\AttributeTok{n =}\NormalTok{ numColors, }\AttributeTok{name =} \StringTok{"Greys"}\NormalTok{)[ ((numColors }\SpecialCharTok{{-}}\NormalTok{ numGroups) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{)}\SpecialCharTok{:}\NormalTok{numColors])}

\NormalTok{allDat }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ rho, }\AttributeTok{y =}\NormalTok{ rho\_hat, }\AttributeTok{color =}\NormalTok{ margins)) }\SpecialCharTok{+}
    \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{size =} \DecValTok{2}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =}\NormalTok{ myColors ) }\SpecialCharTok{+}
    \FunctionTok{geom\_abline}\NormalTok{(}\AttributeTok{slope =} \DecValTok{1}\NormalTok{, }\AttributeTok{linetype =} \StringTok{"dashed"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Specified Correlation"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Estimated Correlation"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ type }\SpecialCharTok{+}\NormalTok{ N, }\AttributeTok{labeller =} \FunctionTok{labeller}\NormalTok{(}\AttributeTok{N =}\NormalTok{ repsLabs, }\AttributeTok{type =}\NormalTok{ typeLabs)) }\SpecialCharTok{+}
    \FunctionTok{theme\_bw}\NormalTok{() }\SpecialCharTok{+}
    \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"bottom"}\NormalTok{, }\AttributeTok{legend.direction =} \StringTok{"horizontal"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dat\_long }\OtherTok{\textless{}{-}}\NormalTok{ benchmark\_dependences }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{total\_time, }\SpecialCharTok{{-}}\NormalTok{n\_sim, }\SpecialCharTok{{-}}\NormalTok{needed\_near\_pd) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(corr\_time}\SpecialCharTok{:}\NormalTok{sim\_time), }\AttributeTok{names\_to =} \StringTok{"Step"}\NormalTok{, }\AttributeTok{values\_to =} \StringTok{"Time"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{dim =} \FunctionTok{factor}\NormalTok{(dim),}
         \AttributeTok{Step =} \FunctionTok{factor}\NormalTok{(Step,}
                       \AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"corr\_time"}\NormalTok{, }\StringTok{"adj\_time"}\NormalTok{, }\StringTok{"admiss\_time"}\NormalTok{, }\StringTok{"sim\_time"}\NormalTok{),}
                       \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Compute Correlation"}\NormalTok{,}
                                  \StringTok{"Adjust Correlation"}\NormalTok{,}
                                  \StringTok{"Check Admissibility"}\NormalTok{,}
                                  \StringTok{"Simulate Data"}\NormalTok{))) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rename}\NormalTok{(}\AttributeTok{Correlation =}\NormalTok{ corr\_type, }\AttributeTok{Dimensions =}\NormalTok{ dim)}

\NormalTok{tabTimes  }\OtherTok{\textless{}{-}}\NormalTok{ dat\_long }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{filter}\NormalTok{(Dimensions }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\DecValTok{100}\NormalTok{, }\DecValTok{250}\NormalTok{, }\DecValTok{500}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{group\_by}\NormalTok{(Dimensions, Correlation) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{summarize}\NormalTok{(}\StringTok{\textquotesingle{}Total Time(Seconds)\textquotesingle{}} \OtherTok{=} \FunctionTok{sum}\NormalTok{(Time)) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{ungroup}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## `summarise()` regrouping output by 'Dimensions' (override with `.groups` argument)
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{tabTimes }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{kable}\NormalTok{(}\AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
          \AttributeTok{linesep =} \FunctionTok{c}\NormalTok{(}\StringTok{""}\NormalTok{, }\StringTok{""}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{addlinespace"}\NormalTok{), }\AttributeTok{format=}\StringTok{"latex"}\NormalTok{,}
          \AttributeTok{col.names =} \FunctionTok{c}\NormalTok{(}\StringTok{"Dimension"}\NormalTok{,}
                        \StringTok{"Correlation type"}\NormalTok{,}
                        \StringTok{"Total Time (Seconds)"}\NormalTok{),}
          \AttributeTok{caption =} \StringTok{\textquotesingle{}Total time to produce 1,000 random vectors with a random correlation matrix and hetereogeneous gamma margins.\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Set colors}
\NormalTok{numColors }\OtherTok{\textless{}{-}} \DecValTok{5}
\NormalTok{numGroups }\OtherTok{\textless{}{-}} \DecValTok{4}
\NormalTok{myColors }\OtherTok{\textless{}{-}} \FunctionTok{rev}\NormalTok{(}\FunctionTok{brewer.pal}\NormalTok{(}\AttributeTok{n=}\NormalTok{numColors, }\AttributeTok{name=}\StringTok{"Greys"}\NormalTok{)[((numColors}\SpecialCharTok{{-}}\NormalTok{numGroups)}\SpecialCharTok{+}\DecValTok{1}\NormalTok{)}\SpecialCharTok{:}\NormalTok{numColors])}

\NormalTok{dat\_long }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{filter}\NormalTok{(Dimensions }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{2500}\NormalTok{, }\DecValTok{5000}\NormalTok{, }\DecValTok{10000}\NormalTok{, }\DecValTok{20000}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{Time (minutes)}\StringTok{\textasciigrave{}} \OtherTok{=}\NormalTok{ Time }\SpecialCharTok{/} \DecValTok{60}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(Correlation, }\StringTok{\textasciigrave{}}\AttributeTok{Time (minutes)}\StringTok{\textasciigrave{}}\NormalTok{, }\AttributeTok{fill=}\NormalTok{Step)) }\SpecialCharTok{+}
    \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{"stack"}\NormalTok{, }\AttributeTok{stat =} \StringTok{"identity"}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{scale\_fill\_manual}\NormalTok{(}\AttributeTok{values =}\NormalTok{ myColors ) }\SpecialCharTok{+}
    \FunctionTok{scale\_y\_continuous}\NormalTok{(}\AttributeTok{breaks =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{80}\NormalTok{, }\DecValTok{10}\NormalTok{),}
                     \AttributeTok{minor\_breaks =} \ConstantTok{NULL}\NormalTok{) }\SpecialCharTok{+}
    \FunctionTok{facet\_grid}\NormalTok{(. }\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dimensions) }\SpecialCharTok{+}
    \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.text.x =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{angle =} \SpecialCharTok{{-}}\DecValTok{90}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{2020{-}02{-}25}\NormalTok{)}
\NormalTok{num\_genes }\OtherTok{\textless{}{-}} \DecValTok{3}
\NormalTok{gene\_sample }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(example\_genes[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{1000}\NormalTok{], num\_genes)}

\FunctionTok{ggpairs}\NormalTok{(}\AttributeTok{data =} \FunctionTok{as.data.frame}\NormalTok{(sim\_nbinom[, gene\_sample]),}
        \AttributeTok{upper =} \FunctionTok{list}\NormalTok{(}\AttributeTok{continuous =} \FunctionTok{wrap}\NormalTok{(}\StringTok{\textquotesingle{}cor\textquotesingle{}}\NormalTok{, }\AttributeTok{method =} \StringTok{"spearman"}\NormalTok{))) }\SpecialCharTok{+} 
  \FunctionTok{theme\_bw}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in cor.test.default(x, y, method = method, use = use): Cannot compute
## exact p-value with ties

## Warning in cor.test.default(x, y, method = method, use = use): Cannot compute
## exact p-value with ties

## Warning in cor.test.default(x, y, method = method, use = use): Cannot compute
## exact p-value with ties
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{include\_graphics}\NormalTok{(}\StringTok{\textquotesingle{}../fig/ch050{-}figBRCA.png\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

>>>>

\author{
    A. Grant Schissler
   \\
    Department of Mathematics \& Statistics \\
    University of Nevada, Reno \\
  Reno, NV 89557 \\
  \texttt{\href{mailto:grant.schissler@gmail.com}{\nolinkurl{grant.schissler@gmail.com}}} \\
   \And
    Edward J. Bedrick
   \\
    University of Arizona \\
   \\
  \texttt{} \\
   \And
    Alexander D. Knudson
   \\
    University of Nevada, Reno \AND \\
   \\
  \texttt{} \\
   \And
    Tomasz J. Kozubowski
   \\
    University of Nevada, Reno \\
   \\
  \texttt{} \\
   \And
    Tin Nguyen
   \\
    University of Nevada, Reno \\
   \\
  \texttt{} \\
   \And
    Anna K. Panorska
   \\
    University of Nevada, Reno \AND \\
   \\
  \texttt{} \\
   \And
    Juli Petereit
   \\
    University of Nevada, Reno \\
   \\
  \texttt{} \\
   \And
    Walter W. Piegorsch
   \\
    University of Arizona \\
   \\
  \texttt{} \\
   \And
    Duc Tran
   \\
    University of Nevada, Reno \\
   \\
  \texttt{} \\
  }

@@

@@

@@

@@

@@

\begin{verbatim}
## Julia Object of type NamedTuple{(:lower, :upper),Tuple{Float64,Float64}}.
## (lower = -0.8816136274594583, upper = 0.8815214379668451)
\end{verbatim}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@
